\papertitle\footnote{Manuscript under review; see \url{http://geoffboeing.com/publications/multiscale-analysis-street-networks/}}

### 2018-02-15 draft/v3/main.tex
update encodings, fonts, headings

%-------------------------------------------------------------------------------------------
% enter the author and paper information below:
%-------------------------------------------------------------------------------------------
\newcommand{\myname}{Geoff Boeing}
\newcommand{\myemail}{gboeing@berkeley.edu}
\newcommand{\myaffiliation}{Department of City and Regional Planning\\University of California, Berkeley}
\newcommand{\paperdate}{February 2018}
\newcommand{\papertitle}{A Multi-Scale Analysis of 27,000 Urban Street Networks}
\newcommand{\papercitation}{Boeing, G. 2018. \papertitle. Under review at \emph{Journal Name}.}
\newcommand{\paperkeywords}{Urban Planning, Transportation, Data Science, Street Networks, Python, OpenStreetMap, Graph Theory, History}

@@

% import these packages first, in order
\usepackage[utf8]{inputenc}
\usepackage[strict,autostyle]{csquotes}
\usepackage[USenglish]{babel}

% import everything else
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{crimson}
\usepackage{datetime}
\usepackage[final]{draftwatermark}
\usepackage{endnotes}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{url}

% location of figure files
\graphicspath{{./figures/}}

% configure the page layout
\geometry{
	paper=letterpaper,         % paper size
	top=3cm,                   % margin sizes
	bottom=3cm,
	left=2.5cm,
	right=2.5cm}
\setlength{\columnsep}{0.75cm} % space between text columns
\setstretch{1.00}              % line spacing
\clubpenalty=10000             % prevent orphans
\widowpenalty=10000            % prevent widows
\let\footnote=\endnote         % turn footnotes into endnotes

@@

\begin{abstract}
OpenStreetMap offers an underexplored source of worldwide geospatial data useful to urban researchers. This study uses the OSMnx software to automatically download and analyze 27,000 US street networks from OpenStreetMap at metropolitan, municipal, and neighborhood scales---namely, every US city and town ($N=19655$), census urbanized area ($N=497$), and Zillow-defined neighborhood ($N=6857$). It presents wide-ranging empirical findings on US urban form and street network characteristics, emphasizing measures relevant to graph theory, urban design, and morphology such as structure, connectedness, density, centrality, and resilience. In the past, street network data acquisition and processing has been challenging and ad hoc. This study illustrates the use of OSMnx and OpenStreetMap to consistently conduct street network analysis with extremely large sample sizes, with clearly defined network definitions and extents for reproducibility, and using nonplanar, directed graphs. These street networks and measures data sets have been shared in a public repository for other researchers to use.
\end{abstract}

@@

\begin{multicols}{2}

@@

This study addresses these limitations by conducting a morphological analysis of urban street networks at multiple scales, with large sample sizes, with clearly defined network definitions and extents for reproducibility, and using nonplanar, directed graphs. In particular, it examines 27,000 urban street networks---represented as primal, nonplanar, weighted multidigraphs with possible self-loops---at multiple overlapping scales across the US, focusing on structure, connectedness, centrality, and resilience. It examines the street networks of every incorporated city and town (population size $N=19655$), census urbanized area ($N=497$), and Zillow-defined neighborhood ($N=6857$) in the US. To do so, it uses OSMnx\footnote{OSMnx is freely available online at \url{https://github.com/gboeing/osmnx}}---a new street network research toolkit \citep{boeing_osmnx:_2017}---to download, construct, and analyze these street networks at metropolitan, municipal, and neighborhood scales. These street networks and measures data sets have been compiled and shared in a public repository at the Harvard Dataverse\footnote{\label{note_data_repo}Data repository available online at \url{https://dataverse.harvard.edu/dataverse/osmnx-street-networks}} for other researchers to repurpose.

@@

@@

\begin{multicols}{2}

>>>>

%-------------------------------------------------------------------------------------------
% enter the author and paper information:
%-------------------------------------------------------------------------------------------
\newcommand{\myname}{Geoff Boeing}
\newcommand{\myemail}{gboeing@berkeley.edu}
\newcommand{\myaffiliation}{Department of City and Regional Planning\\University of California, Berkeley}
\newcommand{\paperdate}{February 2018}
\newcommand{\papertitle}{A Multi-Scale Analysis of 27,000 Urban Street Networks}
\newcommand{\papercitation}{Boeing, G. 2018. \papertitle. Under review at \emph{Journal Name}.}
\newcommand{\paperkeywords}{Urban Planning, Transportation, Data Science, Street Networks, Python, OpenStreetMap, Graph Theory, History}

@@

% import encoding and font packages for pdflatex, in order
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{crimson}
\usepackage{helvet}

% import language and regionalization packages, in order
\usepackage[strict,autostyle]{csquotes}
\usepackage[USenglish]{babel}
\usepackage{microtype}

% import everything else
\usepackage{authblk}
\usepackage{booktabs}
\usepackage[final]{draftwatermark}
\usepackage{endnotes}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{url}

% location of figure files, via graphicx package
\graphicspath{{./figures/}}

% configure the page layout, via geometry package
\geometry{
    paper=letterpaper,         % paper size
    top=3cm,                   % margin sizes
    bottom=3cm,
    left=2.5cm,
    right=2.5cm}
\setlength{\columnsep}{0.75cm} % space between columns
\setstretch{1.00}              % line spacing
\clubpenalty=10000             % prevent orphans
\widowpenalty=10000            % prevent widows

% set section/subsection headings as the sans serif font
\titleformat{\section}{\normalfont\sffamily\large\bfseries\color{black}}{\thesection.}{0.3em}{}
\titleformat{\subsection}{\normalfont\sffamily\small\bfseries\color{black}}{\thesubsection.}{0.3em}{}

@@

\begin{abstract}
OpenStreetMap offers an underexplored source of worldwide geospatial data useful to urban researchers. This study uses the OSMnx software to automatically download and analyze 27,000 US street networks from OpenStreetMap at metropolitan, municipal, and neighborhood scales---namely, every US city and town, census urbanized area, and Zillow-defined neighborhood. It presents empirical findings on US urban form and street network characteristics, emphasizing measures relevant to graph theory, transportation, urban design, and morphology such as structure, connectedness, density, centrality, and resilience. In the past, street network data acquisition and processing have been challenging and ad hoc. This study illustrates the use of OSMnx and OpenStreetMap to consistently conduct street network analysis with extremely large sample sizes, with clearly defined network definitions and extents for reproducibility, and using nonplanar, directed graphs. These street networks and measures data have been shared in a public repository for other researchers to use.
\end{abstract}

@@

% start two-column layout after the title and abstract
\begin{multicols}{2}

@@

This study addresses these limitations by conducting a morphological analysis of urban street networks at multiple scales, with large sample sizes, with clearly defined network definitions and extents for reproducibility, and using nonplanar, directed graphs. In particular, it examines 27,000 urban street networks---represented as primal, nonplanar, weighted multidigraphs with possible self-loops---at multiple overlapping scales across the US, focusing on structure, connectedness, centrality, and resilience. It examines the street networks of every incorporated city and town (population size $N=19655$), census urbanized area ($N=497$), and Zillow-defined neighborhood ($N=6857$) in the US. To do so, it uses OSMnx\endnote{OSMnx is freely available online at \url{https://github.com/gboeing/osmnx}}---a new street network research toolkit \citep{boeing_osmnx:_2017}---to download, construct, and analyze these street networks at metropolitan, municipal, and neighborhood scales. These street networks and measures data sets have been compiled and shared in a public repository at the Harvard Dataverse\endnote{\label{note_data_repo}Data repository available online at \url{https://dataverse.harvard.edu/dataverse/osmnx-street-networks}} for other researchers to repurpose.

@@

% switch back to one-column layout to rotate this wide table sideways

@@

% done with wide rotated table, switch back to two columns
\begin{multicols}{2}
